Social Computing Article\thanks{This title is temporary}

### 2013-01-06 Article.tex
Fiz um esboço da introdução

Introduction

>>>>

For years multi-agent systems have been used to research cooperation as a tool for problem-solving. Recently, however, there has been an increasing interest in the use of human beings as problem-solving agents. Several studies have been conducted in which subjects are connected in a network with the goal of searching for the solution of a specific problem, and those have helped shed some light on the way humans interact in order to solve problems.

The experiments conducted by \cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question. The behaviour observed in that study has provided evidence that human beings in a cooperative problem-solving environment might not evaluate solutions proposed by their peers, instead choosing the most readily available one.

Another result of those observations is that there is a higher probability of individuals copying peers' solutions when those are shared by several neighbours, referred to as an evidence of \emph{conformist behaviour}. A similar behaviour was observed in \cite{mason:collablearnet} for a different problem.

We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem} with the aim of verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
